Recruiting Chapter

### 2020-10-26 manuscript.Rmd
draft changes

```{r plot_g_2mode_privu, echo=FALSE, out.width = '100%'}
knitr::include_graphics("assets/figures/plot_g_2mode_privu.pdf")
```
As shown in Figure \@ref(fig:plot_g_2mode_privu), the la la la

>>>>

As shown in Figure \@ref(fig:two-mode-plot).

```{r two-mode-plot, fig.align = 'center', out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
```

plot_g_2mode.pdf
